---
title: "15.458 Project B Ce Luo"
output: html_notebook
---

Set the working directory and read the queried data
```{r}
# set the working directory for RStudio
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

# read the data
ProjBData <- read.csv("proj_queryB_1.txt", header=T)

# str(ProjBData)
# head(ProjBData)

ProjBData$TradeDate <- as.Date(ProjBData$TradeDate, "%m/%d/%Y")
head(ProjBData)
```

Reshape/pivot the panel data
```{r}
# require(tidyverse)
# 
# wideProjBData <- pivot_wider(ProjBData,id_cols=c(TradeDate,id), names_from=id, values_from=r)
# head(wideProjBData)
# row.names(wideProjBData) <- wideProjBData$TradeDate
require(tidyr)
wideProjBData <- spread(ProjBData[,c(1,4,6)], key = id, value = r)
# head(wideProjBData)
row.names(wideProjBData) <- wideProjBData$TradeDate
head(wideProjBData)
```

Weights calculation
```{r}
get_weights_1 <- function(return_vector){
  return_vector <- as.numeric(exp(return_vector) - 1)
  simple_mean <- mean(return_vector)
  signalRaw <- -(return_vector - simple_mean)
  # Record the top and the bottom quintile
  bottomQuintile <- as.numeric(signalRaw <= quantile(signalRaw, probs = seq(0,1,0.2))[2])
  topQuintile <- as.numeric(signalRaw >= quantile(signalRaw, probs = seq(0,1,0.2))[5])
  # Short the bottom, equal weights
  weightsBottom <- -(bottomQuintile/sum(bottomQuintile))
  # Long the top, equal weights
  weightsTop <- topQuintile/sum(topQuintile)
  weights <- weightsBottom + weightsTop
  return(weights)
}

# Calculating Weights 
weights_1 <- t(apply(wideProjBData[,2:ncol(wideProjBData)], 1, get_weights_1))
head(weights_1[,1:9])

# Won't see return on the last day's weights
final_weights_1 <- weights_1[1:(nrow(weights_1)-1),]
# head(final_weights_1[,1:5])
# No weights on the first day's return
final_returns_1 <- wideProjBData[2:(nrow(wideProjBData)), 2:ncol(wideProjBData)]
# head(final_returns_1[,1:5])
```

Form the portfolio returns with plot
```{r}
portfolios_1 <- final_weights_1 * final_returns_1
# head(portfolios_1[,1:10])
portfolios_dailyRet_1 <- apply(portfolios_1, 1, sum)
# head(portfolios_dailyRet_1)
# portfolios_dailyRet_1 <- data.frame(portfolios_dailyRet_1)


require(ggplot2)
# Convert to data frame for ggplot
portfolios_dailyRet_1P <- data.frame(portfolios_dailyRet_1)

qplot(as.Date(row.names(portfolios_dailyRet_1P)), portfolios_dailyRet_1P[,1], geom = c("point", "line")) + labs(title="Daily Strategy Returns",x="Date",y="Portfolio Return")

# mkt return except the first day for comparison
mktDailyRet <- apply(wideProjBData[-1,2:ncol(wideProjBData)], 1, mean)

qplot(as.Date(row.names(portfolios_dailyRet_1P)), mktDailyRet, geom = c("point", "line")) + labs(title="Daily Market Returns",x="Date",y="Market Return")


```

Basic return analysis
```{r}
retAnnualInfo <- function(returns) {
  mean <- 252*mean(returns) * 100
  print(paste("Annualised Mean:", round(mean,2), "%"))
  sd <- sqrt(252)*sd(returns) * 100
  print(paste("Annualised Standard Deviation:", round(sd,2), "%"))
  sr <- mean/sd
  print(paste("Annualised Sharpe Ratio:", round(sr,2)))
  return(c(mean, sd, sr))
}

print("For the strategy:")
retAnnualInfo(portfolios_dailyRet_1)
writeLines("")

print("For the market:")

# str(mktDailyRet)
retAnnualInfo(mktDailyRet)
```

Stationarity test
```{r}
require(tseries)
# ADF test for stationarity
adf.test(portfolios_dailyRet_1)
adf.test(mktDailyRet)
# Concludes both stationary

# KPSS test for stationarity (the null is stationary)
kpss.test(portfolios_dailyRet_1, null = c("Level"), lshort = TRUE)
kpss.test(mktDailyRet, null = c("Level"), lshort = TRUE)

# Results contradictory to the ADF test. The series can be non-stationary, but not unit root non-stationary.
```

Check unusual market event and unusual stock
```{r}
# Use Median Absolute Deviation as a criterion for a more robust result
mktDailyMed <- median(mktDailyRet)
mktDailyMAD <- 5 * mad(mktDailyRet, constant = 1.4826) 
# The constant default 1.4826 is the default, approximating normal SD. 2.5 multilier is usually taken to detect outliers. Taking 5 here for really unusual mkt event

mktUnusual <- mktDailyRet[which(abs(mktDailyRet-mktDailyMed) > mktDailyMAD)]
print("Market unusual:")
print(mktUnusual[order(abs(mktUnusual), decreasing = TRUE)])
writeLines("")

# For stock outliers everyday
getStockOutliers <- function(return_vector){
  retMed <- median(return_vector)
  retMAD <- 5 * mad(mktDailyRet, constant = 1.4826)
  outliers <- as.numeric(abs(return_vector - retMed) > retMAD)
  return(outliers)
}

stockOutliers_1 <- t(apply(wideProjBData[,2:ncol(wideProjBData)], 1, getStockOutliers))
head(stockOutliers_1[,1:10],10)
head(wideProjBData[,1:10], 10)
# 10488 (ALGI) is an obvious outlier for several periods

# Check overall strategy returns without the outliers
get_returns_NoOutliers_1 <- function(return_vector){
  outliers <- getStockOutliers(return_vector)
  # Set 0 return for the outliers, or maybe the median of those that are not outliers
  return_vector[which(outliers == 1)] = median(return_vector[which(outliers == 0)]) 
  return(return_vector)
}

get_weights_NoOutliers_1 <- function(return_vector){
  ret_NoOutliers <- get_returns_NoOutliers_1(return_vector)
  return(get_weights_1(ret_NoOutliers))
}

returns_NoOutliers_1 <- t(apply(wideProjBData[,2:ncol(wideProjBData)], 1, get_returns_NoOutliers_1))
# head(returns_NoOutliers_1[,1:9])

weights_NoOutliers_1 <- t(apply(wideProjBData[,2:ncol(wideProjBData)], 1, get_weights_NoOutliers_1))
# head(weights_NoOutliers_1[,1:9])

# Won't see return on the last day's weights
final_weights_NoOutliers_1 <- weights_NoOutliers_1[1:nrow(weights_NoOutliers_1)-1,]
# head(final_weights_NoOutliers_1[,1:5])
# No weights on the first day's return
final_returns_NoOutliers_1 <- returns_NoOutliers_1[2:(nrow(returns_NoOutliers_1)),]
# head(final_returns_NoOutliers_1[,1:5])

portfolios_NoOutliers_1 <- final_weights_NoOutliers_1 * final_returns_NoOutliers_1
# head(portfolios_NoOutliers_1[,1:10])
portfolios_dailyRet_NoOutliers_1 <- apply(portfolios_NoOutliers_1, 1, sum)
# head(portfolios_dailyRet_NoOutliers_1)

writeLines("")
print("Strategy without outliers")
retAnnualInfo(portfolios_dailyRet_NoOutliers_1)
# Very different



```

Market correlation with and without outliers
```{r}
print("With outliers:")
cor.test(mktDailyRet, portfolios_dailyRet_1)

writeLines("")


dailyRet_NoOutliers <- t(apply(wideProjBData[-1,2:ncol(wideProjBData)], 1, get_returns_NoOutliers_1))

mktDailyRet_NoOutliers <- apply(dailyRet_NoOutliers, 1, mean)

print("Without outliers:")
cor.test(mktDailyRet_NoOutliers, portfolios_dailyRet_NoOutliers_1)
```

For correlation between the long and the short portfolios
```{r}
final_weights_1_long <- final_weights_1
final_weights_1_long[which(final_weights_1_long<0)] <- 0
portfolios_1_long <- final_weights_1_long * final_returns_1
portfolios_dailyRet_1_long <- apply(portfolios_1_long, 1, sum)

final_weights_1_short <- final_weights_1
final_weights_1_short[which(final_weights_1_short>0)] <- 0
portfolios_1_short <- final_weights_1_short * final_returns_1
portfolios_dailyRet_1_short <- apply(portfolios_1_short, 1, sum)

print("With outliers:")
cor.test(portfolios_dailyRet_1_long , portfolios_dailyRet_1_short)

final_weights_NoOutliers_1_long <- final_weights_NoOutliers_1
final_weights_NoOutliers_1_long[which(final_weights_NoOutliers_1_long < 0)] <- 0
portfolios_NoOutliers_1_long <- final_weights_NoOutliers_1_long * final_returns_NoOutliers_1
portfolios_dailyRet_NoOutliers_1_long <- apply(portfolios_NoOutliers_1_long, 1, sum)

final_weights_NoOutliers_1_short <- final_weights_NoOutliers_1
final_weights_NoOutliers_1_short[which(final_weights_NoOutliers_1_short > 0)] <- 0
portfolios_NoOutliers_1_short <- final_weights_NoOutliers_1_short * final_returns_NoOutliers_1
portfolios_dailyRet_NoOutliers_1_short <- apply(portfolios_NoOutliers_1_short, 1, sum)

print("Without outliers")
cor.test(portfolios_dailyRet_NoOutliers_1_long , portfolios_dailyRet_NoOutliers_1_short)
```

Part (g) There are some zero returns for some stock, which probably means that it was not, or no longer, traded in the market in that day. I may influence the quintiles and make simulated performance deviate from what it would be. Also the timing of the trades.

Problem 2
```{r}

contrarian_KDays <- function(wideProjBData, lag = 1){
  
  # Get weights for lag-th day weights
  get_weights_1 <- function(return_vector){
    return_vector <- as.numeric(exp(return_vector) - 1)
    simple_mean <- mean(return_vector)
    signalRaw <- -(return_vector - simple_mean)
    # Record the top and the bottom quintile
    bottomQuintile <- as.numeric(signalRaw <= quantile(signalRaw, probs = seq(0,1,0.2))[2])
    topQuintile <- as.numeric(signalRaw >= quantile(signalRaw, probs = seq(0,1,0.2))[5])
    # Short the bottom, equal weights
    weightsBottom <- -(bottomQuintile/sum(bottomQuintile))
    # Long the top, equal weights
    weightsTop <- topQuintile/sum(topQuintile)
    weights <- weightsBottom + weightsTop
    return(weights)
  }

  # Calculating Weights 
  weights_1 <- t(apply(wideProjBData[,2:ncol(wideProjBData)], 1, get_weights_1))
  
  # Won't see return on the last day's weights, no weights for the first (k-1) days, maps to kth day return instead
  final_weights_1 <- weights_1[ 1:(nrow(weights_1)-lag),]
  # final_weights_1 <- weights_1[lag:(nrow(weights_1)-1),]
  # head(final_weights_1[,1:5])
  # No weights on the first k day's return
  final_returns_1 <- wideProjBData[(1+lag):(nrow(wideProjBData)), 2:ncol(wideProjBData)]
  
  portfolios_1 <- final_weights_1 * final_returns_1
  portfolios_dailyRet_1 <- apply(portfolios_1, 1, sum)
  
  retAnnualInfo <- function(returns) {
    mean <- 252*mean(returns) * 100
    print(paste("Anualised Mean:", round(mean,2), "%"))
    sd <- sqrt(252)*sd(returns) * 100
    print(paste("Annualised Standard Deviation:", round(sd,2), "%"))
    sr <- mean/sd
    print(paste("Annualised Sharpe Ratio:", round(sr,2)))
    return(c(mean, sd, sr))
  }

  print(sprintf("For the strategy (%d-day lag, with outliers):", lag))
  print(retAnnualInfo(portfolios_dailyRet_1))
  writeLines("")
  
  # For stock outliers everyday
  getStockOutliers <- function(return_vector){
    retMed <- median(return_vector)
    retMAD <- 5 * mad(mktDailyRet, constant = 1.4826)
    outliers <- as.numeric(abs(return_vector - retMed) > retMAD)
    return(outliers)
  }
  
  stockOutliers_1 <- t(apply(wideProjBData[,2:ncol(wideProjBData)], 1, getStockOutliers))
  
  # Check overall strategy returns without the outliers
  get_returns_NoOutliers_1 <- function(return_vector){
    outliers <- getStockOutliers(return_vector)
    # Set 0 return for the outliers, or maybe the median of those that are not outliers
    return_vector[which(outliers == 1)] = median(return_vector[which(outliers == 0)]) 
    return(return_vector)
  }
  
  get_weights_NoOutliers_1 <- function(return_vector){
    ret_NoOutliers <- get_returns_NoOutliers_1(return_vector)
    return(get_weights_1(ret_NoOutliers))
  }
  
  returns_NoOutliers_1 <- t(apply(wideProjBData[,2:ncol(wideProjBData)], 1, get_returns_NoOutliers_1))
  
  weights_NoOutliers_1 <- t(apply(wideProjBData[,2:ncol(wideProjBData)], 1, get_weights_NoOutliers_1))
  
  # Won't see return on the last day's weights, no weights for the first (k-1) days, maps to the kth day return instead
  final_weights_NoOutliers_1 <- weights_NoOutliers_1[1:(nrow(weights_NoOutliers_1)-lag),]
  # print(dim(final_weights_NoOutliers_1))
  # No weights on the first k day's return
  final_returns_NoOutliers_1 <- returns_NoOutliers_1[(1+lag):(nrow(returns_NoOutliers_1)),]
  # print(dim(final_returns_NoOutliers_1))
  
  # For output later
  colnames(final_weights_NoOutliers_1) <- colnames(final_returns_NoOutliers_1)
  
  portfolios_NoOutliers_1 <- final_weights_NoOutliers_1 * final_returns_NoOutliers_1
  portfolios_dailyRet_NoOutliers_1 <- apply(portfolios_NoOutliers_1, 1, sum)
  
  print(sprintf("For the strategy (%d-day lag, without outliers):", lag))
  print(retAnnualInfo(portfolios_dailyRet_NoOutliers_1))
  writeLines("")
  return(final_weights_NoOutliers_1) # Get the final_weights as required; decide to process the outliers.
}



```

Output strategy results and save the weights table
```{r}
pid <- 916979573
vid <- 1
outputrows <- 1:30

contrarianWeights_longer <- function(k){
  weights <- contrarian_KDays(wideProjBData, lag = k)
  weights_longer <- pivot_longer(cbind(row.names(weights), as.data.frame(weights)), cols = 2:(dim(weights)[2]+1), names_to = "id", values_to = "w")
  colnames(weights_longer)[1] <- 'd'
  weights_longer <- cbind(pid, weights_longer[,1:2], k, weights_longer[,3], vid)
  weights_longer <- weights_longer[abs(weights_longer$w)>0, ]
  return(weights_longer)
}

weights_projB <- NULL
for (k in 1:5){
  weightsK <- contrarianWeights_longer(k)
  weights_projB <- rbind(weights_projB, weightsK)
}

# dim(weights_projB)
outputrows <- 1:dim(weights_projB)[1]
output_file <- sprintf("ProjBWeights_CeLuo_v%d.txt", vid)
write.table(weights_projB[outputrows,],file=output_file,sep="\t",eol="\r\n",quote=FALSE,row.names=FALSE,col.names=TRUE,append=FALSE)



```


Playing with Modified Strategies 
```{r}
require(zoo)

# signal based on k days cumulative sum log return, weight proportional to the deviation from the cross-sectional median
contrarian_KDaysCum <- function(wideProjBData, k = 3, proportionalWeights = TRUE){
  
  get_weights_1 <- function(cumReturn_vector){
    cumReturn_vector <- as.numeric(exp(cumReturn_vector) - 1)
    simple_median <- median(cumReturn_vector)
    signalRaw <- -(cumReturn_vector - simple_median)
    # Record the top and the bottom quintile
    bottomQuintile <- signalRaw <= quantile(signalRaw, probs = seq(0,1,0.2))[2]
    topQuintile <- signalRaw >= quantile(signalRaw, probs = seq(0,1,0.2))[5]
    # Short the bottom
    weightsBottom <- -(bottomQuintile/sum(bottomQuintile))
    # Long the top
    weightsTop <- topQuintile/sum(topQuintile)
    if (proportionalWeights) {
      weightsBottom[which(bottomQuintile)] <- -(signalRaw[which(bottomQuintile)]/sum(signalRaw[which(bottomQuintile)]))
      # print(weightsBottom)
      weightsTop[which(topQuintile)] <- (signalRaw[which(topQuintile)]/sum(signalRaw[which(topQuintile)]))
      # print(weightsTop)
    }
    weights <- weightsBottom + weightsTop
    return(weights)
  }
  
  # Leave out the tradeDate column
  wideKDaysCumRet <- rollapply(wideProjBData[,-1], width = k, align = "right", FUN = sum, fill = NA)
  if (k>1) wideKDaysCumRet[1:(k-1),] <- 0.1 # set the first (k-1) rows to be zero for NA and divide by 0 issues

  # Calculating Weights 
  weights_1 <- t(apply(wideKDaysCumRet, 1, get_weights_1))
  # print(weights_1)
  
  # Won't see return on the last day's weights, no weights for the first (k-1) days
  final_weights_1 <- weights_1[k:(nrow(weights_1)-1),]
  # print(final_weights_1)
  # No weights on the first k day's return
  final_returns_1 <- wideProjBData[(1+k):(nrow(wideProjBData)), 2:ncol(wideProjBData)]
  # print(final_returns_1)
  
  portfolios_1 <- final_weights_1 * final_returns_1
  portfolios_dailyRet_1 <- apply(portfolios_1, 1, sum)
  # print(head(portfolios_dailyRet_1))
  
  retAnnualInfo <- function(returns) {
    mean <- 252*mean(returns) * 100
    print(paste("Anualised Mean:", round(mean,2), "%"))
    sd <- sqrt(252)*sd(returns) * 100
    print(paste("Annualised Standard Deviation:", round(sd,2), "%"))
    sr <- mean/sd
    print(paste("Annualised Sharpe Ratio:", round(sr,2)))
    return(c(mean, sd, sr))
  }

  print(sprintf("For the strategy (%d-day cumulative, with outliers):", k))
  print(retAnnualInfo(portfolios_dailyRet_1))
  writeLines("")
  
  # mkt return except the first k days for comparison
  mktDailyRet <- apply(wideProjBData[-(1:k),2:ncol(wideProjBData)], 1, mean)
  print("With outliers:")
  print(cor.test(mktDailyRet, portfolios_dailyRet_1))
  
  final_weights_1_long <- final_weights_1
  final_weights_1_long[which(final_weights_1_long<0)] <- 0
  portfolios_1_long <- final_weights_1_long * final_returns_1
  portfolios_dailyRet_1_long <- apply(portfolios_1_long, 1, sum)
  
  final_weights_1_short <- final_weights_1
  final_weights_1_short[which(final_weights_1_short>0)] <- 0
  portfolios_1_short <- final_weights_1_short * final_returns_1
  portfolios_dailyRet_1_short <- apply(portfolios_1_short, 1, sum)
  
  print("With outliers:")
  print(cor.test(portfolios_dailyRet_1_long , portfolios_dailyRet_1_short))
  
  # For stock outliers everyday
  getStockOutliers <- function(return_vector){
    retMed <- median(return_vector)
    retMAD <- 5 * mad(mktDailyRet, constant = 1.4826)
    outliers <- as.numeric(abs(return_vector - retMed) > retMAD)
    return(outliers)
  }
  
  stockOutliers_1 <- t(apply(wideProjBData[,2:ncol(wideProjBData)], 1, getStockOutliers))
  
  # Check overall strategy returns without the outliers
  get_returns_NoOutliers_1 <- function(return_vector){
    outliers <- getStockOutliers(return_vector)
    # Set 0 return for the outliers, or maybe the median of those that are not outliers
    return_vector[which(outliers == 1)] = median(return_vector[which(outliers == 0)]) 
    return(return_vector)
  }
  
  get_weights_NoOutliers_1 <- function(return_vector){
    ret_NoOutliers <- get_returns_NoOutliers_1(return_vector)
    return(get_weights_1(ret_NoOutliers))
  }
  
  returns_NoOutliers_1 <- t(apply(wideProjBData[,-1], 1, get_returns_NoOutliers_1))
  
  weights_NoOutliers_1 <- t(apply(wideKDaysCumRet, 1, get_weights_NoOutliers_1))
  
  # Won't see return on the last day's weights, no weights for the first (k-1) days
  final_weights_NoOutliers_1 <- weights_NoOutliers_1[k:(nrow(weights_NoOutliers_1)-1),]
  # No weights on the first k day's return
  final_returns_NoOutliers_1 <- returns_NoOutliers_1[(1+k):(nrow(returns_NoOutliers_1)),]
  
  # For output later
  # colnames(final_weights_NoOutliers_1) <- colnames(final_returns_NoOutliers_1)
  
  portfolios_NoOutliers_1 <- final_weights_NoOutliers_1 * final_returns_NoOutliers_1
  portfolios_dailyRet_NoOutliers_1 <- apply(portfolios_NoOutliers_1, 1, sum)
  
  print(sprintf("For the strategy (%d-day cumulative, without outliers):", k))
  print(retAnnualInfo(portfolios_dailyRet_NoOutliers_1))
  writeLines("")
  # return(final_weights_NoOutliers_1) # Get the final_weights as required; decide to process the outliers.
  
  dailyRet_NoOutliers <- t(apply(wideProjBData[-(1:k),2:ncol(wideProjBData)], 1, get_returns_NoOutliers_1))
  mktDailyRet_NoOutliers <- apply(dailyRet_NoOutliers, 1, mean)
  print("Without outliers:")
  print(cor.test(mktDailyRet_NoOutliers, portfolios_dailyRet_NoOutliers_1))
  
  final_weights_NoOutliers_1_long <- final_weights_NoOutliers_1
  final_weights_NoOutliers_1_long[which(final_weights_NoOutliers_1_long < 0)] <- 0
  portfolios_NoOutliers_1_long <- final_weights_NoOutliers_1_long * final_returns_NoOutliers_1
  portfolios_dailyRet_NoOutliers_1_long <- apply(portfolios_NoOutliers_1_long, 1, sum)
  
  final_weights_NoOutliers_1_short <- final_weights_NoOutliers_1
  final_weights_NoOutliers_1_short[which(final_weights_NoOutliers_1_short > 0)] <- 0
  portfolios_NoOutliers_1_short <- final_weights_NoOutliers_1_short * final_returns_NoOutliers_1
  portfolios_dailyRet_NoOutliers_1_short <- apply(portfolios_NoOutliers_1_short, 1, sum)
  
  print("Without outliers")
  print(cor.test(portfolios_dailyRet_NoOutliers_1_long , portfolios_dailyRet_NoOutliers_1_short))
}

# Should be the same as before
# contrarian_KDaysCum(wideProjBData, k = 1, proportionalWeights = FALSE)

# contrarian_KDaysCum(wideProjBData[1:15,1:8], k = 5, proportionalWeights = TRUE)

for (i in 1:5){
  contrarian_KDaysCum(wideProjBData, k = i, proportionalWeights = TRUE)
}






```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
