---
title: "15.458 Assignment 1 Code by Ce Luo"
output: html_notebook
---

Problem 1
Read the quantmod package and load the S&P 500 data from Yahoo finance
```{r}
require(quantmod)
# Using Yahoo Finance
# S&P500 Ticker is ^GSPC
symbol = "^GSPC"
startDate = as.Date("1900-01-01")
endDate = as.Date("2020-09-06")
loadSymbols(Symbols = symbol, 
            src = "yahoo",
            from = startDate,
            to = endDate)
head(GSPC)
tail(GSPC)
```

Part (a): from the above output, we can see the date range obtained was from 1927-12-30 to 2020-09-04. With open-close and high-low columns, I consider the data set as complete in terms of replicating Professor Andrew Lo's claim in the article.

Part (b):
```{r}
# Data pre-processing
# Check for missing data
apply(GSPC, MARGIN = 2, FUN = function(x) sum(is.na(x)))

# Check for repetition
diff_close = diff(GSPC$GSPC.Close)
length(index(diff_close[which(diff_close == 0)]))
# index(diff_close[which(diff_close == 0)])

# The index value was small in the early 1900s, and they are not really relevant to our purposes here. Thus, tentatively, I just check the potential repetitions after 1960s.
GSPC[which(diff_close == 0 & index(GSPC) > as.Date("1960-01-01")),]

# Also take a look at high equal to low for real repetitions
length(which(GSPC$GSPC.High == GSPC$GSPC.Low & index(GSPC) > as.Date("1960-01-01")))
tail(GSPC[which(GSPC$GSPC.High == GSPC$GSPC.Low),])

# Check for Negative Values
sapply(GSPC, FUN = function(x) sum(x < 0))
sapply(GSPC, FUN = function(x) sum(x <= 0))

```
Regarding data errors, the most obvious one is the 0 volume for early data. Secondly, there are 540 real repetitions where high is equal to low while there is a non-trivial trading volume. These two information losses can't not be corrected without using alternative data source.

Part (c): I decide to proceed with the sample of non-zero trading volume and day high not equal to day low, assuming the remaining sample is a more accurate representation of the market high low behavior. 
```{r}
validRange <- which(GSPC$GSPC.Volume != 0 & GSPC$GSPC.High != GSPC$GSPC.Low)
# head(GSPC[validRange,])
GSPCProcessed <- GSPC[validRange,]

openHigh <- length(which(GSPCProcessed$GSPC.High==GSPCProcessed$GSPC.Open))/dim(GSPCProcessed)[1]
print(paste('Prob(P_high = P_open):  ', openHigh))
closeHigh <- length(which(GSPCProcessed$GSPC.High==GSPCProcessed$GSPC.Close))/dim(GSPCProcessed)[1]
print(paste('Prob(P_high = P_close):  ', closeHigh))
openLow <- length(which(GSPCProcessed$GSPC.Low==GSPCProcessed$GSPC.Open))/dim(GSPCProcessed)[1]
print(paste('Prob(P_low = P_open):  ', openLow))
closeLow <- length(which(GSPCProcessed$GSPC.Low==GSPCProcessed$GSPC.Close))/dim(GSPCProcessed)[1]
print(paste('Prob(P_low = P_close):  ', closeLow))


```

Random walk is non-stationary and its variance increases with time. Therefore, theoretically, if the price follows a simple random walk, the high and low should probably occur a little more at the closing than at the opening due to the extra conditional variance. On the other hand, for random walk with drift, which breaks the symmetry, it can be hard to set the drift parameter to test the null hypothesis. However, in this case, we see that both p_high and p_low happen more frequently at the open (8.89% and 10.56% respectively) than at the close (4.21% and 1.26% respectively) , so it also indicates the evidence of overreaction at the market opening and mean reversion, which goes against the random walk hypothesis.

Part (d): 
```{r}
GSPCProcessed$intraRange <-  (GSPCProcessed$GSPC.High- GSPCProcessed$GSPC.Low)/ GSPCProcessed$GSPC.Low
GSPCProcessedSub <- GSPCProcessed[which(index(GSPCProcessed) >= '1980-01-01' & index(GSPCProcessed) <= '2011-08-30'),]
dCount <- 0
for (i in 1:20){
  print(GSPCProcessedSub[order(-GSPCProcessedSub$intraRange)[i],])
  if (index(GSPCProcessedSub[order(-GSPCProcessedSub$intraRange)[i],]) >= '2008-09-01') {
    dCount <- dCount + 1
  }
}
writeLines("")
print(paste(dCount, 'occurred during the final three-year sub-period'))

```
From the above results, 15 occurred during the final three-year sub-period.

Part (e): 
```{r}
GSPCProcessed$OverntRet <-  (GSPCProcessed$GSPC.Open - lag(GSPCProcessed$GSPC.Close, k = 1))/lag(GSPCProcessed$GSPC.Close, k = 1)
# head(GSPCProcessed)
# GSPCProcessed$OverntRet[1] = 0 # Set the first to be zero to avoid potential NA issue
GSPCProcessedSub <- GSPCProcessed[which(index(GSPCProcessed) >= '1980-01-01' & index(GSPCProcessed) <= '2011-08-30'),]
# GSPCProcessedSub[sample(nrow(GSPCProcessedSub), 7), ]
t20PosOverntRet <- GSPCProcessedSub[order(-GSPCProcessedSub$OverntRet)[1:20],]
print("Top 20 positive overnight returns:")
for (i in 1:20){
  # print(GSPCProcessedSub[order(-GSPCProcessedSub$OverntRet)[i],])
  print(t20PosOverntRet[order(index(t20PosOverntRet)),][i])
}
writeLines("")
t20NegOverntRet <- GSPCProcessedSub[order(GSPCProcessedSub$OverntRet)[1:20],]
print("Top 20 negative overnight returns:")
for (i in 1:20){
  # print(GSPCProcessedSub[order(GSPCProcessedSub$OverntRet)[i],])
  print(t20NegOverntRet[order(index(t20NegOverntRet)),][i])
}

```
 
Based on the above results, there are 8 among top 20 positive overnight returns during the three-year period from 1980-01-01 to 1982-12-31, which is followed by the period from 2008-09-01 to 2011-8-30 that has 7 top positive overnight returns. On the other hand, the ending period of 2008-09-01 to 2011-8-30 has the most negative overnight returns--10 among the top 20.

Part (f):
```{r}
GSPCProcessed$logReturn <- log(GSPCProcessed$GSPC.Close/lag(GSPCProcessed$GSPC.Close, k = 1))
# head(GSPCProcessed)
GSPCProcessed$logReturn[1] = 0 # Set the first to be zero to avoid potential NA issue
# for (i in 1:dim(GSPCProcessed)[1]){
#   thisDate <- index(GSPCProcessed[i,])
#   GSPCProcessed$PriorSD[i] <- sd( GSPCProcessed$logReturn[as.Date((as.Date(thisDate)-63):(as.Date(thisDate-1)))] )
#   # Be careful of index conversion, may get shifted
# }

# Calculate the sd of the prior 63 trading days (unnecessary to scale by sqrt(252) as we are comparing daily returns for ordering)
GSPCProcessed$PriorSD <- lag(rollapply(GSPCProcessed$logReturn, width = 63, align = "right", FUN = sd, fill = NA), k = 1)

GSPCProcessed$jumpMeas <- GSPCProcessed$logReturn/GSPCProcessed$PriorSD

# head(GSPCProcessed)
# tail(GSPCProcessed)

GSPCProcessedSub <- GSPCProcessed[which(index(GSPCProcessed) >= '1980-01-01' & index(GSPCProcessed) <= '2011-08-30'),]
fCount <- 0
print("Top 20 jumps:")
for (i in 1:20){
  print(GSPCProcessedSub[order(-abs(GSPCProcessedSub$jumpMeas))[i],])
  if (index(GSPCProcessedSub[order(-abs(GSPCProcessedSub$jumpMeas))[i],]) >= '2008-09-01') {
    fCount <- fCount + 1
  }
}
writeLines("")
print(paste(fCount, 'occurred during the final three-year sub-period'))
```
From the above results, 5 occurred during the final three-year sub-period.


Problem 2
Besides the GSPC data used in problem 1, the following spreadsheet containing SPX and VFINX (an old S&P 500 index fund) is constructed through Bloomberg data. 
```{r}
# GSPCProcessed["1982-10-05",]
GSPCProcessed["1982-10-06",]
# GSPCProcessed["1982-10-07",]

SPX_VFINX <- read.csv("P2.csv", skip = 5, header = TRUE)
# str(SPX_VFINX)
# head(SPX_VFINX)
# tail(SPX_VFINX)
row.names(SPX_VFINX) <- SPX_VFINX$Dates

# print(SPX_VFINX["10/5/1982",])
print(SPX_VFINX["10/6/1982",])
# print(SPX_VFINX["10/7/1982",])

```

The difference between the open prices of GSPC from Yahoo and SPX from Bloomberg on 10/6/1982 is 0.02/121.98 = 0.016%, which is probably trivial. However, the difference between the close prices does show 1/125.97= 0.8% discrepancy, which looks quite significant for daily values or returns. 

To resolve the discrepancy, I decide to refer to VFINX, an S&P 500 index fund, to see which daily return is consistent with VFINX's market return on 10/6/1982. It turns out that the simple return of VFINX on 10/6/1982 was 3.2755%, which is consistent with its open and close prices (15.57 and 16.08 respectively) and the simple return of GSPC (e^0.03218-1 = 0.0327) on that day. Therefore, I decide to trust the GSPC data, i.e., I believe that the correct close price was 125.97. 


