---
title: "15.458 Project B Ce Luo"
output: html_notebook
---

Problem #1
Set the working directory and read the queried data
```{r}
# set the working directory for RStudio
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

# read the data
ProjC_1_Data <- read.csv("projC_query0.txt", header=T)

# str(ProjC_1_Data)
# head(ProjC_1_Data)

ProjC_1_Data$Date <- as.Date(ProjC_1_Data$Date, "%Y-%m-%d")
head(ProjC_1_Data)
```

1.a
A time series plot of the 3-month rolling beta of the stock vs. the S&P 500.
```{r}
require(ggplot2)

plot1aCoeff <- 0.1
ggplot(data = ProjC_1_Data, aes(Date)) + geom_line(aes(y = Beta, colour = "3-month Beta")) +geom_line(aes(y = SPTR/plot1aCoeff, colour = "SPTR")) +
scale_y_continuous(name = "For Beta", sec.axis = sec_axis(~.*plot1aCoeff, name="For SPTR"))+ labs(title="For Walmart",x="Date")


```

1.b
A scatter plot of 1-day stock returns vs. the SPTR (S&P 500 total return index) 1-day returns along with a line of best fit
```{r}
require(ggpmisc)
ggplot(data = ProjC_1_Data, aes(x = SPTR, y = Return)) + geom_point() + geom_smooth(method = "lm", formula = y ~ x) + labs(title="For Walmart")+ stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```

1.c
A scatter plot of 1-day stock returns vs. the VIX (CBOE implied volatility index) 1-day returns along with regression line and its slope equation.
```{r}
ggplot(data = ProjC_1_Data, aes(x = VIX, y = Return)) + geom_point() + geom_smooth(method = "lm", formula = y ~ x) + labs(title="For Walmart") + stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```

Should VIX be an additional factor other than the mkt?
```{r}
vixOnMkt_1 <- lm(VIX ~ SPTR, data = ProjC_1_Data)
require(lmtest)
coeftest(vixOnMkt_1, vcov = NeweyWest(vixOnMkt_1, lag = 6, adjust = T, verbose=T))
# Insignicate intercept, probably shouldn't be considered as another "factor"

```


Problem #2
2.a
Give the annualized return, volatility, and Sharpe ratio (using rf=0) for the strategy.
```{r}
require(readxl)

# Read the strategy return data copied from portfolio analysis sheet
C2_strategyRet <- read_excel('ProjC2.xlsx', sheet = 1, col_names = TRUE)
# head(C2_strategyRet)
C2_strategyRet$`Row Labels` <- as.Date(C2_strategyRet$`Row Labels`, '%m/%d/%Y')

retAnnualInfo <- function(returns, rf = 0) {
  mean <- 252*mean(returns) * 100
  print(paste("Annualized Mean:", round(mean,2), "%"))
  sd <- sqrt(252)*sd(returns) * 100
  print(paste("Annualized Standard Deviation:", round(sd,2), "%"))
  sr <- (mean-rf)/sd
  print(paste("Annualized Sharpe Ratio:", round(sr,2)))
  return(c(mean, sd, sr))
}

colnames(C2_strategyRet)[4] <- "StrategyRet"
retAnnualInfo(C2_strategyRet$StrategyRet)

```

2.b & c
Use linear regression to report on the CAPM alpha, beta, and R-squared for the strategy, including standard errors of your estimates and t-statistics.

Then extend this regression model to include Fama-French factors.
```{r}
# Read the FF3 data
C2_FF <- read.csv('ProjC2_query1.txt', header = TRUE)
# head(C2_FF)
C2_FF$d <- as.Date(C2_FF$d, '%Y-%m-%d')

# Merge into a dataframe 
colnames(C2_strategyRet)[1] <- "d"
C2_dataMerged <- merge(C2_strategyRet, C2_FF, by = c("d"))
# head(C2_dataMerged)

require(lmtest)
require(sandwich)
print("For CAPM:")
CAPM2b <- lm(StrategyRet ~ mktrf, data = C2_dataMerged)
coeftest(CAPM2b, vcov = NeweyWest(CAPM2b, lag = 6, adjust = T, verbose=T))
summary(CAPM2b)

print("For FF3:")
CAPM2c <- lm(StrategyRet ~ mktrf + smb + hml, data = C2_dataMerged)
coeftest(CAPM2c, vcov = NeweyWest(CAPM2c, lag = 6, adjust = T, verbose=T))
summary(CAPM2c)


```

2.d
Plot the strategy one-day returns in order, from lowest to highest.
```{r}
# ggplot(data = C2_dataMerged, aes(x = d[order(StrategyRet)], y = sort(StrategyRet))) + geom_point()
qplot(StrategyRet, data = C2_dataMerged)

# Define winner based on market excess return
C2_dataMerged$win <- as.numeric(C2_dataMerged$StrategyRet > C2_dataMerged$mktrf)

print(sprintf("Fraction of winners: %f", length(which(C2_dataMerged$win == 1))/dim(C2_dataMerged)[1]))
print(sprintf("Fraction of losers: %f", length(which(C2_dataMerged$win == 0))/dim(C2_dataMerged)[1]))
writeLines("")

# qplot(StrategyRet, data = C2_dataMerged, geom = c("boxplot")) + coord_flip()
qplot( x = factor(win), y = StrategyRet, data = C2_dataMerged, geom = c("boxplot")) + labs(title = "Boxplot for 'losers' and 'Winners' ")

print(sprintf("Median of winners: %f", median(C2_dataMerged$StrategyRet[which(C2_dataMerged$win == 1)]) ))
print(sprintf("Median of losers: %f", median(C2_dataMerged$StrategyRet[which(C2_dataMerged$win == 0)]) ))

```

Problem #3
3.a
```{r}
# Read the strategy return data copied from portfolio analysis sheet
C3_strategyRet <- read_excel('ProjC3.xlsx', sheet = 1, col_names = TRUE)
# head(C3_strategyRet)
C3_strategyRet$`Row Labels` <- as.Date(C3_strategyRet$`Row Labels`, '%m/%d/%Y')

colnames(C3_strategyRet)[4] <- "StrategyRet"
print("For strategy overall:")
retAnnualInfo(C3_strategyRet$StrategyRet)
writeLines("")

print("For long positions:")
retAnnualInfo(C3_strategyRet$Long)
writeLines("")

print("For short positions:")
retAnnualInfo(C3_strategyRet$Short)
writeLines("")

```

3.b
Use linear regression to report on the CAPM alpha, beta, and R-squared for the strategy, including standard errors of your estimates and t-statistics.

```{r}
# Read the FF3 data
C3_FF <- read.csv('ProjC3_query1.txt', header = TRUE)
# head(C3_FF)
C3_FF$d <- as.Date(C3_FF$d, '%Y-%m-%d')

# Merge into a dataframe 
colnames(C3_strategyRet)[1] <- "d"
C3_dataMerged <- merge(C3_strategyRet, C3_FF, by = c("d"))
# head(C3_dataMerged)

print("For CAPM:")
CAPM3b <- lm(StrategyRet ~ mktrf, data = C3_dataMerged)
coeftest(CAPM3b, vcov = NeweyWest(CAPM3b, lag = 6, adjust = T, verbose=T))
summary(CAPM3b)

print("For FF3:")
CAPM3c <- lm(StrategyRet ~ mktrf + smb + hml, data = C3_dataMerged)
coeftest(CAPM3c, vcov = NeweyWest(CAPM3c, lag = 6, adjust = T, verbose=T))
summary(CAPM3c)

```

3.c
Plot the strategy one-day returns in order, from lowest to highest.
```{r}
qplot(StrategyRet, data = C3_dataMerged)

# Define winner based on market excess return
C3_dataMerged$win <- as.numeric(C3_dataMerged$StrategyRet > C3_dataMerged$mktrf)

print(sprintf("Fraction of winners: %f", length(which(C3_dataMerged$win == 1))/dim(C3_dataMerged)[1]))
print(sprintf("Fraction of losers: %f", length(which(C3_dataMerged$win == 0))/dim(C3_dataMerged)[1]))
writeLines("")

qplot( x = factor(win), y = StrategyRet, data = C3_dataMerged, geom = c("boxplot")) + labs(title = "Boxplot for 'losers' and 'Winners' ")

print(sprintf("Median of winners: %f", median(C3_dataMerged$StrategyRet[which(C3_dataMerged$win == 1)]) ))
print(sprintf("Median of losers: %f", median(C3_dataMerged$StrategyRet[which(C3_dataMerged$win == 0)]) ))

```


Problem 4 Data
4.a 
For each GICS sector, give its highest and lowest net exposure over the period 2005-2009.
```{r}

c4a_long <- read_excel("ProjC4a.xlsx", sheet = 1, col_names = TRUE)
c4a_long$TradeDate <- as.Date(c4a_long$TradeDate, "%m/%d/%Y")
head(c4a_long)

require(tidyr)

c4a_wide <- spread(c4a_long, key = Sector, value = Weight)

# head(c4a_wide)

maxIgnoreNA <- function(x){
  return(max(x, na.rm = TRUE))
}

minIgnoreNA <- function(x){
  return(min(x, na.rm = TRUE))
}

sectorMax <- apply(c4a_wide[,-1], MARGIN=2, maxIgnoreNA)
sectorMin <- apply(c4a_wide[,-1], MARGIN=2, minIgnoreNA)

print("Highest net exposure: ")
sectorMax

writeLines("")

print("Lowest net exposure: ")
sectorMin


```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
